---
title: "Data Science Fundamentals: Data Prep"
author: "Rachel Greenlee"
date: "10/8/2021"
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    toc_depth: 1
    theme: sandstone
    fig_width: 8
    fig_height: 5
  pdf_document:
    toc: yes
    toc_depth: '1'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(skimr) # nice alternative to summary() for seeing dataset at a glance
library(dplyr) # for piping function! other tools for manipulating datasets
```


# 1. Identify the goal 

## Subheading w/o tabs underneath

# 2. Obtain the data

## Various Methods {.tabset}

### CSV

To load in a .csv file from your local computer in the working directory. You can also use this method and paste a link in to an active webpage that display the csv data (like a github page when you click 'raw'). 

Link to chocolate kaggle page here: https://www.kaggle.com/rtatman/chocolate-bar-ratings?select=flavors_of_cacao.csv

```{r}
# reading in chocolate dataset from kaggle that I downloaded to data-raw folder
chocolate <- read.csv(file = "data-raw/flavors_of_cacao.csv")
```


### Web scraping

# 3. Data cleaning

## Consideration {.tabset}

### Rename variables

To rename all the columns in one go, in order, use colnames:

```{r}
colnames(chocolate) <- c('company', 'bean_origin_or_bar_name', 'id', 'review_year', 'cocoa_perc', 'company_location',
                         'rating', 'bean_type', 'broad_bean_origin')
```

To rename select columns via index or current name:

```{r}
# rename via dplyr


# rename(new_name = old_name,
#         new_name2 = old_name2)

# by index
# colnames(df)[index_column] <- new_name
```



### NAs



### Save cleaned data file

```{r}
write.csv(chocolate,"data-clean/chocolate.csv", row.names = FALSE)
```


### Variable types

# 4. Exploratory data analysis

## Options {.tabset}

### Tables

```{r}
skim(chocolate)
```


### Graphics

# 5. Transforming variables

## When & how {.tabset}

### Skewness

### Other things

# 6. Feature enginerring

## Derived variables

## Dummy variables

# 7. Create test and training sets


